### 2025-08-05 mycv/cv_latex.tex
update

        \normalsize
        \mbox{Department of Materials Science and Metallurgy, Changwon National University}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:yjeong@changwon.ac.kr}{yjeong@changwon.ac.kr}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+82-55-214-3694}{+82-55-214-3694}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/youngung}{github.com/youngung}}%
    \end{header}

@@

        \section{Goverment-funded projects}
        \begin{twocolentry}{2023 - 2027}
            \textbf{Mid-career Researcher Program (PI), National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2020 - 2027}
            \textbf{BK21, National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2018 - 2024}
            \textbf{Engieering Research Center, National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2020 - 2023}
            \textbf{General Research Program (PI), National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2018 - 2020}
            \textbf{Virtual engineering platform project, Ministry of Trade, Industry and Energy}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2017 - 2020}
            \textbf{General Research Program (PI), National Research Foundation of Korea}
        \end{twocolentry}

>>>>

        \normalsize
        \mbox{Department of Materials Science and Metallurgy, Changwon National University}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:yjeong@changwon.ac.kr}{yjeong@changwon.ac.kr}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+82-55-214-3694}{+82-55-214-3694}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{https://youngung.github.io}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/youngung}{https://github.com/youngung}}%
    \end{header}

@@

        \section{Goverment-funded projects}
        \begin{twocolentry}{2023 - 2027}
            \textbf{Mid-career Researcher Program (PI), National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2020 - 2027}
            \textbf{BK21, National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2018 - 2024}
            \textbf{Engineering Research Center, National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2020 - 2023}
            \textbf{General Research Program (PI), National Research Foundation of Korea}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2018 - 2020}
            \textbf{Virtual engineering platform project, Ministry of Trade, Industry and Energy}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{2017 - 2020}
            \textbf{General Research Program (PI), National Research Foundation of Korea}
        \end{twocolentry}
